On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-06 arity1upper.tex
fix pyramid pic

Let us fix some common starting points for the next two subsections. Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|+1$. We will argue about the situation when the first bead is stabilized outside $\hexagon_p^n$ (a hexagon of radius $n$). Let this be the $i$th bead of the transcript. Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that bead $i$ is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
\begin{figure}
	\centering
	\includegraphics[width=0.3\linewidth]{./Fig/hexagonOut}
	\caption{$\hexagon_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
	\label{fig:hexagonOut}
\end{figure}

@@

As before, let us assume that the last bead stabilized within $\hexagon_p^n$ is at point $(0,0)$ and the next bead is the first to be stabilized outside $\hexagon_p^n$ at point $(1,1)$. Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.\\
%\begin{enumerate}
\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand. If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities (see Fig.~\ref{fig:beadi2}, except it starts from (0,0) not (1,1)). Therefore, it needs to make three new bonds to deterministically stabilize $i$. There are five possible cases in which beads $i, i+1, i+2$ can add three bonds, see Fig.~\ref{fig:3bonds}. In the cases (b) and (e) in Fig.~\ref{fig:3bonds}, there are beads having a free hand at (1,0) and (-1,0) already stabilized before bead $i-1$ is fixed at (0,0). One of these two beads may be a predecessor of bead $i-1$, but at least one of them is not. When bead $i-1$ is fixed at (0,0), it makes a bond with the one of these two beads which is not its predecessor. This means that it is impossible to have three beads at (-1,0), (0,0) and (1,0), each with a free hand, when bead $i$ is fixed, and consequently, cases (b) and (e) in Fig.~\ref{fig:3bonds} cannot occur. Case (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1). If it makes three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, it will need to make three bonds forever to be deterministic. Similarly to case 1. in the previous section, cases (a) and (c) in Fig.~\ref{fig:3bonds} lead to nondeterministism eventually, when the transcript reaches a first corner of $\hexagon_p^n$.

>>>>

Let us fix some common starting points for the next two subsections. Let the point where the first transcript bead was fixed be $p$ and let $n=|\mathrm{seed}|$. We will argue about the situation when the first bead is stabilized outside $\hexagon_p^n$ (a hexagon of radius $n$). Let this be the $i$th bead of the transcript. Without loss of generality, we can translate the origin $(0,0)$ to the coordinates of bead $i-1$ (which is still in $\hexagon_p^n$), and we can assume that bead $i$ is fixed at $(1,1)$ (see Fig.~\ref{fig:hexagonOut}).
\begin{figure}
	\centering
	\includegraphics[width=0.3\linewidth]{./Fig/hexagonOut}
	\caption{$\hexagon_p^n$ and the position $(1,1)$ of the first bead fixed outside of it.}
	\label{fig:hexagonOut}
\end{figure}

@@

As before, let us assume that the last bead stabilized within $\hexagon_p^n$ is at point $(0,0)$ and the next bead is the first to be stabilized outside $\hexagon_p^n$ at point $(1,1)$. Depending on whether bead $i-1$ at point (0,0) has a free hand to form a bond or not, we distinguish two cases.\\
%\begin{enumerate}
\noindent\textbf{Case 1.}  Bead $i-1$ at (0,0) has a free hand. If the most stable conformation formed by beads $i, i+1, i+2$ adds only two  bonds, it will be nondeterministic because there are at least two possibilities (see Fig.~\ref{fig:beadi2}, except it starts from (0,0) not (1,1)). Therefore, it needs to make three new bonds to deterministically stabilize $i$. There are five possible cases in which beads $i, i+1, i+2$ can add three bonds, see Fig.~\ref{fig:3bonds}. In the cases (b) and (e) in Fig.~\ref{fig:3bonds}, there are beads having a free hand at (1,0) and (-1,0) already stabilized before bead $i-1$ is fixed at (0,0). One of these two beads may be a predecessor of bead $i-1$, but at least one of them is not. When bead $i-1$ is fixed at (0,0), it makes a bond with the one of these two beads which is not its predecessor. This means that it is impossible to have three beads at (-1,0), (0,0) and (1,0), each with a free hand, when bead $i$ is fixed, and consequently, cases (b) and (e) in Fig.~\ref{fig:3bonds} cannot occur. Case (d) in Fig.~\ref{fig:3bonds} becomes nondeterministic when bead $i$ is fixed because bead $i$ can be fixed at (-1,0) and bond with (-2,0), bead $i+1$ can be placed (0,1) and bond with (0,0) and bead $i+2$ can be placed (1,1) and bond with (0,1). If three consecutive beads make three bonds once, such as (a) and (c) in Fig.~\ref{fig:3bonds}, then each consecutive triple from here on will need to make three bonds to be deterministic. Therefore, similarly to case 1. in the previous section, cases (a) and (c) in Fig.~\ref{fig:3bonds} lead to nondeterminism eventually, when the transcript reaches a first corner of $\hexagon_p^n$.
